%\chapterimage{sam.jpg}
\chapter{Appendix}\index{Appendix}
\renewcommand{\chaptername}{}
%\addcontentsline{toc}{chapter}{\textcolor{PittGold}{Appendix}}

\section*{Publications}\index{Publications}
\subsection*{SaM Staff}
\input{SaM_publications}

\subsection*{SaM Users}
\begin{enumerate}

\item R.\ D.\ Kennedy, D.\ J.\ Clingerman, W.\ J.\ Morris,
  C.\ E.\ Wilmer, A.\ A.\ N.\ Sarjeant, C.\ L.\ Stern,
  M.\ A.\ O'Keeffe, R.\ Q.\ Snurr, J.\ T.\ Hupp, O.\ K.\ Farha,
  C.\ A.\ Mirkin, ``Metallacarborane-Based Metal-Organic Framework
  with a Complex Topology,'' \textit{Crystal Growth and Design},
  vol.\ \textbf{14}, no.\ 3, pp.\ 1324--1330 (2014).

\item Y.\ J.\ Col\'{o}n, D.\ Fair\'{e}n-Jim\'{e}nez, C.\ E.\ Wilmer,
  R.\ Q.\ Snurr, ``High-Throughput Screening of Porous Crystalline
  Materials for Hydrogen Storage Capacity Near Room Temperature,''
  \textit{Journal of Physical Chemistry C}, vol.\ \textbf{118},
  no.\ 10, pp.\ 5383--5389 (2014).
  
\item Y.\ Bae, J.\ Liu, C.\ E.\ Wilmer, H.\ Sun, A.\ N.\ Dickey,
  M.\ Kim, A.\ I.\ Benin, R.\ R.\ Willis, D.\ Barpaga, M.\ D.\ LeVan,
  R.\ Q.\ Snurr, ``The Effect of Pyridine Modification of Ni-DOBDC on
  $\mathrm{CO}_2$ Capture under Humid Conditions,'' \textit{Chemical
    Communications}, vol. \ \textbf{50}, no.\ 25, pp. 3296--3298
  (2014).
  
\item O.\ Karagiaridi, W.\ Bury, D.\ Fair\'{e}n-Jim\'{e}nez,
  C.\ E.\ Wilmer, A.\ A.\ N.\ Sarjeant, J.\ T.\ Hupp, O.\ K.\ Farha,
  ``Enhanced Gas Sorption Properties and Unique Behavior Toward Liquid
  Water in a Pillared-Paddlewheel Metal-Organic Framework
  Transmetalated with Ni(II),'' \textit{Inorganic Chemistry},
  vol.\ \textbf{53}, no.\ 19, pp.\ 10432--10436 (2014).

\item D.\ A.\ G\'{o}mez-Gualdr\'{o}n, C.\ E.\ Wilmer, O.\ K.\ Farha,
  J.\ T.\ Hupp, R.\ Q.\ Snurr, ``Exploring the Limits of Methane
  Storage and Delivery in Nanoporous Materials,'' \textit{Journal of
    Physical Chemistry C}, vol.\ \textbf{118}, no.\ 13,
  pp.\ 6941--6951 (2014).

\item P.\ Zhang, A.\ To, ``Highly Enhanced Damping Figure of Merit in
  Biomimetic Hierarchical Staggered Composites,'' \textit{ASME Journal
    of Applied Mechanics}, vol.\ \textbf{81}, p.\ 051015 (2014).

\item Q.\ Yang, E.\ Biyikli, A.\ To, ``Multiresolution Molecular
  Mechanics: Convergence and Error Structure Analysis,''
  \textit{Computer Methods and Applied Mechanics and Engineering},
  vol.\ \textbf{269}, pp.\ 20--45 (2014).

\item A.\ Giri, J.\ Tao, M.\ Kirca, A.\ To, ``Compressive Behavior and
  Deformation Mechanism of Nanoporous Open-Cell Foam with Ultrathin
  Ligaments,'' \textit{Journal of Nanomechanics and Micromechanics},
  vol.\ \textbf{4}, no.\ 2, p.\ A4013012 (2014).

\item Y.\ Fu, A.\ To, ``A Modification to Hardy's Thermomechanical
  Theory that Conserves Fundamental Properties More Accurately:
  Tensile and Shear Failures in Iron,'' \textit{Modeling and
    Simulation in Materials Science and Engineering},
  vol.\ \textbf{22}, p.\ 015010 (2014).

\item E.\ Biyikli, Q.\ Yang, A.\ To, ``Multiresolution Molecular
  Mechanics: Dynamics,'' \textit{Computer Methods in Applied Mechanics
    and Engineering}, vol.\ \textbf{274}, pp.\ 42--55 (2014).

\item D.\ Mohammadyani, H.\ Modarress, A.\ To, A.\ Amani,
  ``Interactions of Fullerenes (C60) and its Hydroxyl Derivatives with
  Lipid Bilayer: A Coarse-Grained Molecular Dynamic Simulation,''
  \textit{Brazilian Journal of Physics}, vol.\ \textbf{44}, pp.\ 1--7
  (2014).

\item X.\ Yang, D.\ Chen, Y.\ Du, A.\ To, ``Heat Conduction in
  Extended X-Junctions of Single-Walled Carbon Nanotubes,''
  \textit{Journal of Physics and Chemistry of Solids},
  vol.\ \textbf{75}, pp.\ 123--129 (2014).

\item X.\ Yang, D.\ Chen, Z.\ Han, ``Effects of Welding on Thermal
  Conductivity of Randomly Oriented Carbon Nanotube Networks,''
  \textit{International Journal of Heat and Mass Transfer},
  vol.\ \textbf{70}, pp.\ 803--810 (2014).

\item A.\ T.\ Celebi, M.\ Kirca, C.\ Baykasoglu, A.\ Mugan, A.\ To,
  ``Tensile Behavior of Heat Welded CNT Network Structures,''
  \textit{Computational Materials Science}, vol.\ \textbf{88},
  pp.\ 14--21 (2014).

\item X.\ Yang, Y.\ Huang, L.\ Wang, Z.\ Han, and A.\ C.\ To, ``Carbon
  Nanotube-Fullerene Hybrid Nanostructures by C60 Bombardment:
  Formation and Mechanical Behavior,'' \textit{Physical Chemistry
    Chemical Physics}, vol.\ \textbf{16}, p.\ 21615 (2014).

\item X.\ Yang, Y.\ Huang, L.\ Wang, Z.\ Han, and A.\ C.\ To,
  ``Nanobuds Promote Heat Welding of Carbon Nanotubes at
  Experimentally-Relevant Temperatures,'' \textit{RSC Advances},
  vol.\ \textbf{4}, pp.\ 56313--56317 (2014).

\item B.\ Zhang, A.\ C.\ T.\ van Duin, J.\ K.\ Johnson, ``Development
  of a ReaxFF Reactive Force Field for Tetrabutylphosphonium
  Glycinate/$\mathrm{CO}_2$ Mixtures,'' \textit{Journal of Physical
    Chemistry B}, vol.\ \textbf{118}, pp.\ 12008--12016 (2014).

\item Z.-Y.\ Hu, X.\ Shao, D.\ Wang, L.-M.\ Liu, and J.\ K.\ Johnson,
  ``A First-Principles Study of Lithium-Decorated Hybrid Boron Nitride
  and Graphene Domains for Hydrogen Storage,'' \textit{Journal of
    Chemical Physics}, vol.\ \textbf{141}, p.\ 084711 (2014).

\item D.-L.\ Chen, N.\ Wang, F.-F.\ Wang, J.\ Xie, Y.\ Zhong, W.\ Zhu,
  J.\ K.\ Johnson, R.\ Krishna, ``Utilizing Gate-Opening Mechanism in
  ZIF-7 for Adsorption Discrimination between $\mathrm{N}_2\mathrm{O}$
  and $\mathrm{CO}_2$,'' \textit{Journal of Physical Chemistry C},
  vol.\ \textbf{118}, pp.\ 17831--17837 (2014).

\item R.\ J.\ Perry, S.\ E.\ Genovese, R.\ L.\ Farnum, I.\ Sultanova,
  T.\ M.\ Perry, M.\ J.\ O'Brien, H.-B.\ Xie, D.-L.\ Chen,
  R.\ M.\ Enick, J.\ K.\ Johnson, S.\ Alshahrani, ``A Combined
  Experimental and Computational Study on Selected Physical Properties
  of Amino Silicones,'' \textit{Industrial \& Engineering Chemistry
    Research}, vol.\ \textbf{53}, pp.\ 1334--1341 (2014).

\item N.\ A.\ Tavenor, K.\ I.\ Silva, S.\ Saxena, W.\ S.\ Horne,
  ``Origins of Structural Flexibility in Protein-Based Supramolecular
  Polymers Revealed by DEER Spectroscopy,'' \textit{Journal of
    Physical Chemistry B}, vol.\ \textbf{118}, pp.\ 9881--9889 (2014).

\item X.\ Yin, E.\ Wierzbinski, H.\ Lu, S.\ Bezer, A.\ R.\ de Leon,
  K.\ L.\ Davis, C.\ Achim, and D.\ H.\ Waldeck, ``A Three-Step
  Kinetic Model for Electrochemical Charge Transfer in the Hopping
  Regime,'' \textit{Journal of Physical Chemistry A},
  vol.\ \textbf{118}, pp.\ 7579--7589 (2014).

\item X.\ Yin, J.\ Kong, A.\ de Leon, Y.\ L.\ Li, Z.\ J.\ Ma,
  E.\ Wierzbinski, C.\ Achim, and D.\ H.\ Waldeck, ``Luminescence
  Quenching by Photoinduced Charge Transfer between Metal Complexes in
  Peptide Nucleic Acids,'' \textit{Journal of Physical Chemistry B},
  vol.\ \textbf{118}, pp.\ 9037--9045 (2014).

\item G.\ P.\ Galdi, M.\ Mohebbi, R.\ Zakerzadeh, P.\ Zunino,
  ``Hyperbolic-Parabolic Coupling in Partially Dissipative Systems,''
  in \textit{Fluid-Structure Interaction and Biomedical Applications},
  editors: T. Bodn\'{a}r, G. P. Galdi and \v{S}. Ne\v{c}asov\'{a},
  Springer Basel, pp.\ 197--256, 2014.

\item R.\ Zakerzadeh, P.\ Zunino, ``Fluid-Structure Interaction in the
  Arteries with a Poroelastic Wall Model,'' in \textit{Proceedings of
    21st Iranian Conference in Biomedical Engineering (ICBME)},
  Tehran, Iran, pp.\ 35--39, November 26-28, 2014.

\item A.\ Vikram, D.\ Lipus, and K.\ Bibby, ``Produced Water Exposure
  Alters Bacterial Response to Biocides,'' \textit{Environmental
    Science and Technology}, vol.\ \textbf{48}, no.\ 21,
  pp.\ 13001--13009 (2014).

\item E.\ Stachler and K.\ Bibby, ``Metagenomic Evaluation of the
  Highly Abundant Human Gut Bacteriophage CrAssphage for Source
  Tracking of Human Fecal Pollution,'' \textit{Environmental Science
    and Technology Letters}, vol.\ \textbf{1}, no.\ 10, pp.\ 405--409
  (2014).

\item A.\ Murali-Mohan, D.\ Lipus, K.\ Bibby, K.\ Gregory, ``The
  Functional Potential of Microbial Communities in Hydraulic
  Fracturing Source Water and Produced Water from Natural Gas
  Extraction Characterized by Metagenomic Sequencing,'' \textit{PLoS
    ONE}, vol.\ \textbf{9}, no.\ 10, p.\ e107682 (2014).

\item E.\ Su\'{a}rez, S.\ Lettieri, M.\ C.\ Zwier, C.\ A.\ Stringer,
  S.\ R.\ Subramanian, L.\ T.\ Chong, and D.\ M.\ Zuckerman,
  ``Simultaneous Computation of Dynamical and Equilibrium Information
  using a Weighted Ensemble of Trajectories,'' \textit{Journal of
    Chemical Theory and Computation}, vol.\ \textbf{10}, no.\ 7,
  pp.\ 2658--2667 (2014).

\item K.\ T.\ Debiec, A.\ M.\ Gronenborn, and L.\ T.\ Chong,
  ``Evaluating the Strength of Salt Bridges - A Comparison of Current
  Biomolecular Force Fields,'' \textit{Journal of Physical Chemistry
    B}, vol.\ \textbf{118}, no.\ 24, pp.\ 6561--6569 (2014).

\item P.\ Li, G.\ Henkelman, J.\ A.\ Keith, J.\ K.\ Johnson,
  ``Elucidation of Aqueous Solvent Mediated Hydrogen Transfer
  Reactions by \textit{ab initio} Molecular Dynamics and Nudged
  Elastic Band Studies of $\mathrm{Na}\mathrm{B}\mathrm{H}_4$
  Hydrolysis,'' \textit{Journal of Physical Chemistry C},
  vol.\ \textbf{118}, no.\ 37, pp.\ 21385--21399 (2014).

\item V.\ K.\ Voora and K.\ D.\ Jordan, ``Non-Valence
  Correlation-Bound Anion State of $\mathrm{C}_6\mathrm{F}_6$: Doorway
  to Low-Energy Electron Capture,'' \textit{Journal of Physical
    Chemistry A}, vol.\ \textbf{118}, no.\ 35, pp.\ 7201--7205 (2014).

\item O.\ Karalti, X.\ Su, W.\ A.\ Al-Saidi, and K.\ D.\ Jordan,
  ``Correcting Density Functionals for Dispersion Interactions using
  Pseudopotentials,'' \textit{Chemical Physics Letters},
  vol.\ \textbf{591}, pp.\ 133--136 (2014).

\item D.\ C.\ Sorescu, S.\ Civi\v{s}, and K.\ D.\ Jordan, ``Mechanism
  of Oxygen Exchange Between $\mathrm{CO}_2$ and
  $\mathrm{Ti}\mathrm{O}_2(101)$ Anatase,'' \textit{Journal of
    Physical Chemistry C}, vol.\ \textbf{118}, pp.\ 1628--1639 (2014).

\item K.\ D.\ Jordan, V.\ K.\ Voora, and J.\ Simons, ``Negative
  Electron Affinities - Fact or Fiction?'' \textit{Theoretical
    Chemistry Accounts}, vol.\ \textbf{133}, no.\ 1445, pp.\ 1--15,
  (2014).

\item M.\ F.\ Falcetta, L.\ A.\ DiFalco, D.\ S.\ Ackerman,
  J.\ C.\ Barlow, and K.\ D.\ Jordan, ``Assessment of Various
  Electronic Structure Methods for Characterizing Temporary Anion
  States: Application to the Ground State Anions of $\mathrm{N}_2$,
  $\mathrm{C}_2\mathrm{H}_2$, $\mathrm{C}_2\mathrm{H}_4$ and
  $\mathrm{C}_6\mathrm{H}_6$,'' \textit{Journal of Physical Chemistry
    A}, vol.\ \textbf{118}, pp.\ 7489--7497 (2014).

\item E.\ M.\ Myshakin, M.\ Makaremi, V.\ N.\ Romanov, K.\ D.\ Jordan,
  and G.\ D.\ Guthrie, ``Molecular Dynamics Simulations of
  Turbostratic Dry and Hydrated Montmorillonite with Intercalated
  Carbon Dioxide,'' \textit{Journal of Physical Chemistry A},
  vol.\ \textbf{118}, pp.\ 7454--7468 (2014).

\item M.\ J.\ Deible, O.\ Tuguldur, and K.\ D.\ Jordan, ``Theoretical
  Study of the Binding Energy of a Methane Molecule in a
  $(\mathrm{H}_2\mathrm{O})20$ Dodecahedral Cage,'' \textit{Journal of
    Physical Chemistry A}, vol.\ \textbf{118}, pp.\ 8257--8263 (2014).

\item N.\ Heine, E.\ G.\ Kratz, R.\ Bergmann, D.\ P.\ Schofield,
  K.\ R.\ Asmis, K.\ D.\ Jordan , and A.\ B.\ McCoy, ``Vibrational
  Spectroscopy of the Water–Nitrate Complex in the
  $\mathrm{O}-\mathrm{H}$ Stretching Region,'' \textit{Journal of
    Physical Chemistry A}, vol.\ \textbf{118}, pp.\ 8188--8197 (2014).

\item V.\ K.\ Voora and K.\ D.\ Jordan, ``Nonvalence Correlation-Bound
  Anion States of Spherical Fullerenes,'' \textit{Nano Letters},
  vol.\ \textbf{14}, pp.\ 4602--4606 (2014).

\item D.\ C.\ Sorescu, E.\ F.\ C.\ Byrd, B.\ M.\ Rice, and
  K.\ D.\ Jordan, ``Assessing the Performances of Dispersion-Corrected
  Density Functional Methods for Predicting the Crystallographic
  Properties of High Nitrogen Energetic Salts,'' \textit{Journal of
    Chemical Theory and Computation}, vol.\ \textbf{10},
  pp.\ 4982--4994 (2014).

\item C.\ S.\ Ewing, S.\ Bhavsar, G.\ Veser, J.\ J.\ McCarthy,
  J.\ K.\ Johnson, ``Accurate Models of Amorphous Silica Surfaces from
  First-Principles Thermodynamics of Surface Dehydroxylation,''
  \textit{Langmuir}, vol.\ \textbf{18}, pp.\ 5133--5141 (2014).

\item K.\ A.\ Werling, M.\ Griffin, G.\ R.\ Hutchison, and
  D.\ S.\ Lambrecht, ``Piezoelectric Hydrogen Bonding: Computational
  Screening for a Design Rationale,'' \textit{Journal of Physical
    Chemistry A}, vol.\ \textbf{118}, no.\ 35, pp.\ 7404--7410 (2014).

\item N.\ Austin and G.\ Mpourmpakis, ``Understanding the Stability,
  Electronic, and Adsorption Properties of Sub-nanometer Group XI
  Monometallic and Bimetallic Catalysts,'' \textit{Journal of Physical
    Chemistry C}, vol.\ \textbf{118}, pp.\ 18521--18528 (2014).

\item P.\ Kostestkyy, J.\ Yu, R.\ J.\ Gorte and G.\ Mpourmpakis,
  ``Structure-Activity Relationships on Metal-Oxides: Alcohol
  Dehydration,'' \textit{Catalysis Science \& Technology},
  vol.\ \textbf{4}, pp.\ 3861--3869 (2014).

\item A.\ N.\ Andriotis, G.\ Mpourmpakis, S.\ Broderick, K.\ Rajan,
  S.\ Datta, M.\ Sunkara, and M.\ Menon, ``Informatics Guided
  Discovery of Surface Structure-Chemistry Relationships in Catalytic
  Nanoparticles,'' \textit{Journal of Chemical Physics},
  vol.\ \textbf{140}, p.\ 094705 (2014).

\item A.\ Yan, Z.\ L.\ Poole, R.\ Chen, P.\ W.\ Leu, P.\ Ohodnicki,
  and K.\ P.\ Chen, ``Scalable Fabrication of Metal Oxide Functional
  Materials and their Applications in High-Temperature Optical
  Sensing,'' \textit{Journal of The Minerals, Metals \& Materials
    Society}, vol.\ \textbf{67}, no.\ 1, pp.\ 53--58 (2014).

\item T.\ Gao, E.\ Stevens, J.-K.\ Lee, and P.\ W.\ Leu, ``Designing
  Metal Hemispheres on Silicon Ultrathin Film Solar Cells for
  Plasmonic Light Trapping,'' \textit{Optics Letters},
  vol.\ \textbf{39}, no.\ 16, pp.\ 4647--4650 (2014).

\item M.\ I.\ Kayes and P.\ W.\ Leu, ``Comparative Study of Absorption
  in Tilted Silicon Nanowire Arrays for Photovoltaics,''
  \textit{Nanoscale Research Letters}, vol.\ \textbf{9}, no.\ 1,
  p.\ 620 (2014).

\item B.\ Ding, T.\ Gao, D.\ Waldeck, P.\ W.\ Leu, and J.-K.\ Lee,
  ``Synergistic Effect of Surface Plasmonic Particles in
  $\mathrm{Pb}\mathrm{S}$/$\mathrm{Ti}\mathrm{O}_2$ Heterojunction
  Solar Cells,'' \textit{Solar Energy Materials and Solar Cells},
  vol.\ \textbf{128}, pp.\ 386--393 (2014).

\item B.\ Wang, E.\ Stevens, and P.\ W.\ Leu, ``Strong Broadband
  Absorption in GaAs Nanocone and Nanowire Arrays for Solar Cells,''
  \textit{Optics Express}, vol.\ \textbf{22}, no.\ S2, pp.\ A386--A395
  (2014).

\item T.\ Gao, B.\ Wang, B.\ Ding, J.-K.\ Lee, and P.\ W.\ Leu,
  ``Uniform and Ordered Copper Nanomeshes by Microsphere Lithography
  for Transparent Electrodes,'' \textit{Nano Letters},
  vol.\ \textbf{14}, no.\ 4, pp.\ 2105--2110 (2014).

\item E.\ Suarez, S.\ Lettieri, M.\ C.\ Zwier, \textit{et al.},
  ``Simultaneous Computation of Dynamical and Equilibrium Information
  using a Weighted Ensemble of Trajectories,'' \textit{Biophysical
    Journal}, vol.\ \textbf{106}, no.\ 2, p.\ 406A (2014).

\item J.\ M.\ Spiriti, D.\ M.\ Zuckerman, ``A New Strategy for
  Coarse-Grained Protein Simulations: Smoothed Energy Tables,''
  \textit{Biophysical Journal}, vol.\ \textbf{106}, no.\ 2, p.\ 412A
  (2014).

\item S.\ R.\ Subramanian, R.\ Palli, D.\ M.\ Zuckerman,
  ``Mixed-Resolution Monte Carlo: A Tool for Sampling Proteins and
  Ligands,'' \textit{Biophysical Journal}, vol.\ \textbf{106}, no.\ 2,
  412A (2014).

\item R.\ Palli, S.\ R.\ Subramanian, D.\ M.\ Zuckerman,
  ``Mixed-Resolution Monte Carlo: Application to Flexible Docking of
  the Estrogen Receptor,'' \textit{Biophysical Journal},
  vol.\ \textbf{106}, no.\ 2, p.\ 475A (2014).

\item V.\ Niemsiri, X.\ Wang, D.\ Pirim, Z.\ H.\ Radwan,
  J.\ E.\ Hokanson, R.\ F.\ Hamman, M.\ M.\ Barmada, F.\ Y.\ Demirci,
  M.\ I.\ Kamboh, ``Impact of Genetic Variants in Human Scavenger
  Receptor Class B Type I (SCARB1) on Plasma Lipid Traits,''
  \textit{Circulation: Cardiovascular Genetics}, vol.\ \textbf{7},
  no.\ 6, pp.\ 838--847 (2014).

\item C.\ S.\ Floudas, N.\ Um, M.\ I.\ Kamboh, M.\ M.\ Barmada,
  S.\ Visweswaran, ``Identifying Genetic Interactions Associated with
  Late-Onset Alzheimer's Disease,'' \textit{BioData Mining},
  vol.\ \textbf{7}, no.\ 1, p.\ 35 (2014).

\item Z.\ H.\ Radwan, X.\ Wang, F.\ Waqar, D.\ Pirim, V.\ Niemsiri,
  J.\ E.\ Hokanson, R.\ F.\ Hamman, C.\ H.\ Bunker, M.\ M.\ Barmada,
  R.\ Y.\ Demirci, M.\ I.\ Kamboh, ``Comprehensive Evaluation of the
  Association of APOE Genetic Variation with Plasma Lipoprotein Traits
  in U.S. Whites and African Blacks,'' \textit{PloS One},
  vol.\ \textbf{9}, no.\ 12, p.\ e114618 (2014).

\item X.\ Zheng, F.\ Y.\ Demirci, M.\ M.\ Barmada, G.\ A.\ Richardson,
  O.\ L.\ Lopez, R.\ A.\ Sweet, M.\ I.\ Kamboh, E.\ Feingold, ``A Rare
  Duplication on Chromosome 16p11.2 is Identified in Patients with
  Psychosis in Alzheimer's Disease,'' \textit{PloS One},
  vol.\ \textbf{9}, no.\ 11, p.\ e111462 (2014).

\item A.\ C.\ Naj, G.\ Jun, C.\ Reitz, B.\ W.\ Kunkle, W.\ Perry,
  Y.\ S.\ Park, G.\ W.\ Beecham, R.\ A.\ Rajbhandary,
  K.\ L.\ Hamilton-Nelson, L.\ S.\ Wang, J.\ S.\ Kauwe,
  M.\ J.\ Huentelman, A.\ J.\ Myers, T.\ D.\ Bird, B.\ F.\ Boeve,
  C.\ T.\ Baldwin, G.\ P.\ Jarvik, P.\ K.\ Crane, E.\ Rogaeva,
  M.\ M.\ Barmada, F.\ Y.\ Demirci, C.\ Cruchaga, P.\ L.\ Kramer,
  N.\ Ertekin-Taner, J.\ Hardy, N.\ R.\ Graff-Radford, R.\ C.\ Green,
  E.\ B.\ Larson, P.\ H.\ St.\ George-Hyslop, J.\ D.\ Buxbaum,
  D.\ A.\ Evans, J.\ A.\ Schneider, K.\ L.\ Lunetta, M.\ I.\ Kamboh,
  A.\ J.\ Saykin, E.\ M.\ Reiman, P.\ L.\ De Jager, D.\ A.\ Bennett,
  J.\ C.\ Morris, T.\ J.\ Montine, A.\ M.\ Goate, D.\ Blacker,
  D.\ W.\ Tsuang, H.\ Hakonarson, W.\ A.\ Kukull, T.\ M.\ Foroud,
  E.\ R.\ Martin, J.\ L.\ Haines, R.\ P.\ Mayeux, L.\ A.\ Farrer,
  G.\ D.\ Schellenberg, M.\ A.\ Pericak-Vance, Alzheimer Disease
  Genetics Consortium, M.\ S.\ Albert, R.\ L.\ Albin,
  L.\ G.\ Apostolova, S.\ E.\ Arnold, R.\ Barber, L.\ L.\ Barnes,
  T.\ G.\ Beach, J.\ T.\ Becker, D.\ Beekly, E.\ H.\ Bigio,
  J.\ D.\ Bowen, A.\ Boxer, J.\ R.\ Burke, N.\ J.\ Cairns,
  L.\ B.\ Cantwell, C.\ Cao, C.\ S.\ Carlson, R.\ M.\ Carney,
  M.\ M.\ Carrasquillo, S.\ L.\ Carroll, H.\ C.\ Chui, D.\ G.\ Clark,
  J.\ Corneveaux, D.\ H.\ Cribbs, E.\ A.\ Crocco, C.\ DeCarli,
  S.\ T.\ DeKosky, M.\ Dick, D.\ W.\ Dickson, R.\ Duara,
  K.\ M.\ Faber, K.\ B.\ Fallon, M.\ R.\ Farlow, S.\ Ferris,
  M.\ P.\ Frosch, D.\ R.\ Galasko, M.\ Ganguli, M.\ Gearing,
  D.\ H.\ Geschwind, B.\ Ghetti, J.\ R.\ Gilbert, J.\ D.\ Glass,
  J.\ H.\ Growdon, R.\ L.\ Hamilton, L.\ E.\ Harrell, E.\ Head,
  L.\ S.\ Honig, C.\ M.\ Hulette, B.\ T.\ Hyman, G.\ A.\ Jicha,
  L.\ W.\ Jin, A.\ Karydas, J.\ A.\ Kaye, R.\ Kim, E.\ H.\ Koo,
  N.\ W.\ Kowall, J.\ H.\ Kramer, F.\ M.\ LaFerla, J.\ J.\ Lah,
  J.\ B.\ Leverenz, A.\ I.\ Levey, G.\ Li, A.\ P.\ Lieberman,
  C.\ F.\ Lin, O.\ L.\ Lopez, C.\ G.\ Lyketsos, W.\ J.\ Mack,
  F.\ Martiniuk, D.\ C.\ Mash, E.\ Masliah, W.\ C.\ McCormick,
  S.\ M.\ McCurry, A.\ N.\ McDavid, A.\ C.\ McKee, M.\ Mesulam,
  B.\ L.\ Miller, C.\ A.\ Miller, J.\ W.\ Miller, J.\ R.\ Murrell,
  J.\ M.\ Olichney, V.\ S.\ Pankratz, J.\ E.\ Parisi, H.\ L.\ Paulson,
  E.\ Peskind, R.\ C.\ Petersen, A.\ Pierce, W.\ W.\ Poon, H.\ Potter,
  J.\ F.\ Quinn, A.\ Raj, M.\ Raskind, B.\ Reisberg, J.\ M.\ Ringman,
  E.\ D.\ Roberson, H.\ J.\ Rosen, R.\ N.\ Rosenberg, M.\ Sano,
  L.\ S.\ Schneider, W.\ W.\ Seeley, A.\ G.\ Smith, J.\ A.\ Sonnen,
  S.\ Spina, R.\ A.\ Stern, R.\ E.\ Tanzi, T.\ A.\ Thornton-Wells,
  J.\ Q.\ Trojanowski, J.\ C.\ Troncoso, O.\ Valladares, V.\ M.\ Van
  Deerlin, L.\ J.\ Van Eldik, B.\ N.\ Vardarajan, H.\ V.\ Vinters,
  J.\ P.\ Vonsattel, S.\ Weintraub, K.\ A.\ Welsh-Bohmer,
  J.\ Williamson, S.\ Wishnek, R.\ L.\ Woltjer, C.\ B.\ Wright,
  S.\ G.\ Younkin, C.\ E.\ Yu, L.\ Yu, ``Effects of Multiple Genetic
  Loci on Age at Onset in Late-Onset Alzheimer Disease: a Genome-Wide
  Association Study,'' \textit{JAMA Neurology}, vol.\ \textbf{71},
  no.\ 11, pp.\ 1394--1404 (2014).

\item J.\ LaRusch, J.\ Jung, I.\ J.\ General, M.\ D.\ Lewis,
  H.\ W.\ Park, R.\ E.\ Brand, A.\ Gelrud, M.\ A.\ Anderson,
  P.\ A.\ Banks, D.\ Conwell, C.\ Lawrence, J.\ Romagnuolo,
  J.\ Baillie, S.\ Alkaade, G.\ Cote, T.\ B.\ Gardner, S.\ T.\ Amann,
  A.\ Slivka, B.\ Sandhu, A.\ Aloe, M.\ L.\ Kienholz, D.\ Yadav,
  M.\ M.\ Barmada, I.\ Bahar, M.\ G.\ Lee, D.\ C.\ Whitcomb,
  ``Mechanisms of CFTR Functional Variants that Impair Regulated
  Bicarbonate Permeation and Increase Risk for Pancreatitis but not
  for Cystic Fibrosis,'' \textit{PLoS Genetics}, vol.\ \textbf{10},
  no.\ 7, p.\ e1004376 (2014).

\item S.\ Kattel and G.\ Wang, ``Beneficial compressive strain for
  oxygen reduction on Pt (111) surface'', \textit{Journal of Chemical
    Physics}, \textbf{141} 124713 (2014).

\item S.\ Kattel and G.\ Wang, ``Reaction pathway for oxygen reduction
  on FeN4 embedded graphene'', \textit{Journal of Physical Chemistry
    Letters}, \textbf{5} 452-456 (2014).

\end{enumerate}


%\section*{PittGrid}\index{PittGrid}
%\begin{enumerate}
%\item First item goes here
%\end{enumerate}

